Harmful Anti-Foreign Sentiments based on Concern for Competition Should be Recognized and Addressed

### 2023-02-17 outputs/paper/paper.qmd
Paper edits

#survey_data <- read_dta(here::here("inputs/data/survey_cleaned.csv"))
```

>>>>

survey_data <- read_csv(here::here("inputs/data/survey_clean.csv"))
```

##Figure 1 not including p value, percentage bar graph, detailed explanation of tercile meanings

```{r}

```

##Figure 2 add prevent bar

```{r}

```

##Table 1 have it coded in completely (check marks), better description of meanings, labels of models (model1, model2,...)

```{r}

```
